Spfy: distributed predictive genomics of E.coli with graph based result linkage

### 2017-08-11 paper-webserver.tex
ADD: some restructuring

\section{IMPLEMENTATION}
% para
% goals: predictive analylitcs in minutes, storage up 50,000-100,000 genomes {}
% drawbacks - big data
Many previous bioinformatics software programs have been developed \textit{ad hoc}, without the use of software engineering principles \cite{de2015trends}.
Such tools were often script-based, with custom data formats, and only suitable for small collections of data \cite{de2015trends}.
While this was acceptable for smaller analyses, bioinformatic pipelines utilizing WGS data are larger and involve linked dependencies, which require the application of systems engineering principles \cite{schatz2015biological}.
Additionally, many subsets of biology now require the analyses of big-data, where the ability to perform computations in real-time, store data in flexible databases, and utilize a common application programming interface (API) linking resources are required \cite{swaminathan2016review}.

@@

% Mention where users / developers can find documentation
A guide to setting up Spfy is provided at \url{https://github.com/superphy/backend} and a developer guide is provided at \url{https://superphy.readthedocs.io/en/latest/}.

>>>>

\section{IMPLEMENTATION}
% para
% goals: predictive analylitcs in minutes, storage up 50,000-100,000 genomes {}

@@

% drawbacks - big data
Many previous bioinformatics software programs have been developed \textit{ad hoc}, without the use of software engineering principles \cite{de2015trends}.
Such tools were often script-based, with custom data formats, and only suitable for small collections of data \cite{de2015trends}.
While this was acceptable for smaller analyses, bioinformatic pipelines utilizing WGS data are larger and involve linked dependencies, which require the application of systems engineering principles \cite{schatz2015biological}.
Additionally, many subsets of biology now require the analyses of big-data, where the ability to perform computations in real-time, store data in flexible databases, and utilize a common application programming interface (API) linking resources are required \cite{swaminathan2016review}.

One of the key goals in developing Spfy is to maintain instantaneity: modern websites have accustomed users to instant results.
We attempt to use innovations in web development and bring a similar experience to Spfy as a predictive genomics platform for \textit{E. coli}.
% Mention where users / developers can find documentation
Spfy's main documentation and codebase are provided at \url{https://github.com/superphy/backend} and a developer guide is provided at \url{https://superphy.readthedocs.io/en/latest/}.
